An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-07-23 Article/EconGrowth2.Rnw
Papers now use Calvin data frame from the EconData package.

<<data, include=FALSE>>=
# Load historical data
# In Rstudio, this paper is generated from it's directory, which is "Article".
# We need to define paths relative to the location of the paper. 
# Relative path to historical data from Article
historicalData <- subset(AllHistData, subset=Source=="Calvin2011") # From the EconData package

# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)

>>>>

<<data, include=FALSE>>=
# Load historical data
historicalData <- Calvin # From the EconData package
# Load coefficients from all models in one large data frame
coeffs_df <- tbl_df(AllCoef)
# Load fitted data from all models in one large data frame
fitted_df <- tbl_df(AllFitted)
